A 2-Norm Condition Number for B\'{e}zier Curve Intersection

### 2019-06-13 doc/paper.tex
Adding clarification on xtilde and ytilde in Theorem 4.1.

Each component \(x(s)\) and \(y(s)\) of a B\'{e}zier curve is a
polynomial in Bernstein form. For such a polynomial
\begin{equation}
p(s) = \sum_{j = 0}^n p_j B_{j, n}(s)
\end{equation}
the (absolute) condition number of evaluation is
\(\widetilde{p}(s) = \sum_{j = 0}^n \left|p_j\right| B_{j, n}(s)\)
(\cite{Farouki1987}) when the parameter \(s\) is in the unit interval.

@@

\begin{theorem}
Let \(\left[\begin{array}{c} \alpha \\ \beta
\end{array}\right]\) be a transversal intersection of two planar
B\'{e}zier curves \(b_0(s)\) and \(b_1(t)\). Define the vectors
\begin{equation}
\widetilde{F}_{+} = \left[ \begin{array}{c}
  \widetilde{x}_0(\alpha) + \widetilde{x}_1(\beta) \\
  \widetilde{y}_0(\alpha) + \widetilde{y}_1(\beta) \end{array}\right] \quad
\text{and} \quad
\widetilde{F}_{-} = \left[ \begin{array}{c}
  \widetilde{x}_0(\alpha) + \widetilde{x}_1(\beta) \\
  -\widetilde{y}_0(\alpha) - \widetilde{y}_1(\beta)\end{array}\right].
\end{equation}
Then the root condition number of the intersection is the
greater of two vector norms:
\begin{equation}\label{eq:kappa-max}
\kappa_{\alpha, \beta} = \frac{1}{\sqrt{\alpha^2 + \beta^2}} \max \left\{
\left \lVert J\left(\alpha, \beta\right)^{-1} \widetilde{F}_{+}\right \rVert_2,
\left \lVert J\left(\alpha, \beta\right)^{-1} \widetilde{F}_{-}\right \rVert_2
\right\}.
\end{equation}
\end{theorem}

>>>>

Each component \(x(s)\) and \(y(s)\) of a B\'{e}zier curve is a
polynomial in Bernstein form. For such a polynomial
\begin{equation}
p(s) = \sum_{j = 0}^n p_j B_{j, n}(s)
\end{equation}
the (absolute) condition number of evaluation is
\begin{equation}\label{eq:p-tilde}
\widetilde{p}(s) = \sum_{j = 0}^n \left|p_j\right| B_{j, n}(s)
\end{equation}
(\cite{Farouki1987}) when the parameter \(s\) is in the unit interval.

@@

\begin{theorem}
Let \(\left[\begin{array}{c} \alpha \\ \beta
\end{array}\right]\) be a transversal intersection of two planar
B\'{e}zier curves \(b_0(s)\) and \(b_1(t)\). Define the vectors
\begin{equation}
\widetilde{F}_{+} = \left[ \begin{array}{c}
  \widetilde{x}_0(\alpha) + \widetilde{x}_1(\beta) \\
  \widetilde{y}_0(\alpha) + \widetilde{y}_1(\beta) \end{array}\right] \quad
\text{and} \quad
\widetilde{F}_{-} = \left[ \begin{array}{c}
  \widetilde{x}_0(\alpha) + \widetilde{x}_1(\beta) \\
  -\widetilde{y}_0(\alpha) - \widetilde{y}_1(\beta)\end{array}\right].
\end{equation}
where the \(\widetilde{x}_i, \widetilde{y}_j\) are as defined in
\eqref{eq:p-tilde}.
Then the root condition number of the intersection is the
greater of two vector norms:
\begin{equation}\label{eq:kappa-max}
\kappa_{\alpha, \beta} = \frac{1}{\sqrt{\alpha^2 + \beta^2}} \max \left\{
\left \lVert J\left(\alpha, \beta\right)^{-1} \widetilde{F}_{+}\right \rVert_2,
\left \lVert J\left(\alpha, \beta\right)^{-1} \widetilde{F}_{-}\right \rVert_2
\right\}.
\end{equation}
\end{theorem}
